Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-02-12 paper.tex
Smaller dumpbell
Remove comments in the table

The test is performed by firstly evaluating the inequation in a cube
$[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
$F_{sss}$ with our algorithm, giving a discretized volume of $400^3$
voxels as the input. For ease of comparison, $F_{sss}$ function is evaluated within $XY$
plane. Pointwise relative error of $F_{sss}$ is on
\cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced
farther than 0.1 (20 pixels) from curves of discontinuity (see
\cref{fig:sss-dumbbell-precise}) is no more than 20\%.
\begin{figure*}[tp]
  \centering
  \subfigure[The dumbbell-like object used in testing of $F_{sss}$ computation]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell.png}
    \label{fig:sss-dumbbell}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-err.png}
    \label{fig:sss-dumbbell-error}}
  \vskip\baselineskip
  \subfigure[$F_{sss}$: precise. The correlation function is undefined (has type
    II discontinuity) at curves A, B and C.]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-precise.png}
    \label{fig:sss-dumbbell-precise}}
  \hfill
  \subfigure[$F_{sss}$: calculated with our approach]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-julia.png}}
  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
    with its precise values. \highlight{Make dumbbell around 20 percent smaller}}
  \label{fig:sss-verification}
\end{figure*}

@@

\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels/voxels) & Image resolution ($\mu m$)
    & $C_{0.5}$ & Comment \\
    \hline
    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 & \\
    Soil & Reconstruction & $500 \times 500 \times 500$ & 0.72 & 0.9431 & Digitally
    magnified \\
    Shale & Reconstruction & $160 \times 160 \times 160$ & 2.25 & 0.8912 & \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9613 & \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions. \highlight{Remove comments?}}
  \label{tab:summary}
\end{table*}
In this section we compute correlation functions for 2- and 3-dimensional
porous media samples. Table \ref{tab:summary} contains information about these samples. Note
that we compute surface correlation functions only for those samples for which
the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the soil) \cite{samarin2023robust}. Images
of the samples are presented on \cref{fig:samples}. On plots of correlation functions for
isotropic samples we provide a family of curves with the first argument of the
correlation function being fixed. For anisotropic samples we provide heatmaps of
correlation functions where anisotropy can be easily observed.
\begin{figure*}[tp]
  \centering
  \subfigure[Sanstone XCT]{
    \includegraphics[width=0.4\linewidth]{images/15581.png}
    \label{fig:sample-sandstone-xct}}
  \hfill
  \subfigure[Sandstone SEM (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.4\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \vskip\baselineskip
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil.png}
    \label{fig:sample-soil}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale.png}
    \label{fig:sample-shale}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

>>>>

The test is performed by firstly evaluating the inequation in a cube
$[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
$F_{sss}$ with our algorithm, giving a discretized volume of $400^3$
voxels as the input. For ease of comparison, $F_{sss}$ function is evaluated within $XY$
plane. Pointwise relative error of $F_{sss}$ is on
\cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced
farther than 0.1 (20 pixels) from curves of discontinuity (see
\cref{fig:sss-dumbbell-precise}) is no more than 20\%.
\begin{figure*}[tp]
  \centering
  \subfigure[The dumbbell-like object used in testing of $F_{sss}$ computation]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell.png}
    \label{fig:sss-dumbbell}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-err.png}
    \label{fig:sss-dumbbell-error}}
  \vskip\baselineskip
  \subfigure[$F_{sss}$: precise. The correlation function is undefined (has type
    II discontinuity) at curves A, B and C.]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-precise.png}
    \label{fig:sss-dumbbell-precise}}
  \hfill
  \subfigure[$F_{sss}$: calculated with our approach]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-julia.png}}
  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
    with its precise values.}
  \label{fig:sss-verification}
\end{figure*}

@@

\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels/voxels) & Image resolution ($\mu m$)
    & $C_{0.5}$ \\
    \hline
    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 \\
    Soil & Reconstruction & $500 \times 500 \times 500$ & 0.72 & 0.9431 \\
    Shale & Reconstruction & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9613 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table*}
In this section we compute correlation functions for 2- and 3-dimensional
porous media samples. Table \ref{tab:summary} contains information about these samples. Note
that we compute surface correlation functions only for those samples for which
the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the soil) \cite{samarin2023robust}. Images
of the samples are presented on \cref{fig:samples}. On plots of correlation functions for
isotropic samples we provide a family of curves with the first argument of the
correlation function being fixed. For anisotropic samples we provide heatmaps of
correlation functions where anisotropy can be easily observed.
\begin{figure*}[tp]
  \centering
  \subfigure[Sanstone XCT]{
    \includegraphics[width=0.4\linewidth]{images/15581.png}
    \label{fig:sample-sandstone-xct}}
  \hfill
  \subfigure[Sandstone SEM (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.4\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \vskip\baselineskip
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil.png}
    \label{fig:sample-soil}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale.png}
    \label{fig:sample-shale}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}
